Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-07-27 doc/thesis/preface.tex
Defence version of thesis with changes

A version of chapter 2 has been submitted for publication with the title
``Reconstructing network parameters from viral phylogenies.'' An oral
presentation entitled ``Phylodynamic inference of contact network parameters
with kernel-ABC'' was given based on chapter 2 to the 23rd HIV Dynamics and
Evolution meeting on April 25, 2016, in Woods Hole, Massachusetts, USA (the
presentation was delivered remotely). A poster based on chapter 2 entitled
``Likelihood-free estimation of contact network parameters from viral
phylogenies'' is scheduled for presentation at the Intelligent Systems for
Molecular Biology meeting on July 8, 2016, in Orlando, Florida, USA.

Use of the BC data is in accordance with an ethics application that was
reviewed and approved by the UBC/Providence Health Care Research Ethics Board
(H07-02559). Rosemary M. McCloskey completed the Tri-Council Policy Statement:
Ethical Conduct for Research Involving Humans Course on Research Ethics (TCPS
2: CORE) tutorial on June 8, 2016.

>>>>

A version of chapter 2 has been submitted for publication with the title
``Reconstructing network parameters from viral phylogenies.'' An oral
presentation entitled ``Phylodynamic inference of contact network parameters
with kernel-ABC'' was given based on chapter 2 to the 23rd HIV Dynamics and
Evolution meeting on April 25, 2016, in Woods Hole, Massachusetts, USA (the
presentation was delivered remotely). A poster based on chapter 2 entitled
``Likelihood-free estimation of contact network parameters from viral
phylogenies'' was presented at the Intelligent Systems for Molecular Biology
meeting on July 8, 2016, in Orlando, Florida, USA.

Use of the BC data is in accordance with an ethics application that was
reviewed and approved by the UBC/Providence Health Care Research Ethics Board
(H07-02559). 
%Rosemary M. McCloskey has completed the Tri-Council Policy Statement: Ethical
%Conduct for Research Involving Humans Course on Research Ethics (TCPS 2: CORE)
%tutorial.
